Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-30 paper.tex
Add diagrams of product launching and trading

\subsection{Launching and Searching Products}
To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}). Each product has a Product Contract to record the trading process.

@@

@@

\subsection{Trading}
Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.

>>>>

\subsection{Launching and Searching Products}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{launching_product}
	\caption{The process of launching a product.}
	\label{fig:launching_product}
\end{figure}

@@

To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}). Each product has a Product Contract to record the trading process.

@@

\subsection{Trading}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{trading_product}
	\caption{The process of the product trading.}
	\label{fig:trading_product}
\end{figure}

The whole trading process is shown in Figure \ref{fig:trading_product}. Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.
